Use of the library \texttt{fitdistrplus} to specify a distribution from non-censored or censored data

### 2009-10-04 inst/doc/intro2fitdistrplus.Rnw
fitdistrplus 0.1-2 with some new things (see file NEWS)
correction of minor erros on .Rd files and try to correct the vignette
change mom method to mme method. TODO man page.

\documentclass[a4paper]{article}
\usepackage[a4paper,textwidth=18cm,textheight=27cm]{geometry}

@@

One or more parametric distributions may then be fitted to the data set, one at a time, using the
fonction \texttt{fitdist}. This function uses the maximum likelihood
method if the argument \texttt{method="mle"} (or if it is omitted) 
or the matching moments method if the argument \texttt{method="mom"}.
When fitting continuous distributions, 
Kolmogorov-Smirnov and Anderson-Darling statistics are computed and corresponding tests are performed when possible. 
Even if less appropriate for continuous distributions, the Chi-squared statistic is
also computed when possible. For this calculation, cells are defined by the argument \texttt{chisqbreaks}
or automatically defined from the data set and from the argument \texttt{meancount} (the approximate mean count per cell)
which is  fixed to $(4n)^{2/5}$ if omitted (with n the length of the data set).  
For more details, see the help of the function \texttt{fitdist}.
Four goodness of fit plots are also provided.

@@

Below is the result of another fit of the same distribution by matching moments.
<<>>=
f1gbis<-fitdist(x1,"gamma",method="mom")
summary(f1gbis)
@

>>>>

\documentclass[a4paper]{article}
% sweave commands for vignette
%\VignetteIndexEntry{Fit parametric distributions on non-censored or censored data}
%\VignettePackage{fitdistrplus}
%\VignetteKeyword{distribution}

\usepackage[a4paper,textwidth=18cm,textheight=27cm]{geometry}

@@

One or more parametric distributions may then be fitted to the data set, one at a time, using the
fonction \texttt{fitdist}. This function uses the maximum likelihood
method if the argument \texttt{method="mle"} (or if it is omitted) 
or the matching moments estimation if the argument \texttt{method="mme"}.
When fitting continuous distributions, 
Kolmogorov-Smirnov and Anderson-Darling statistics are computed and corresponding tests are performed when possible. 
Even if less appropriate for continuous distributions, the Chi-squared statistic is
also computed when possible. For this calculation, cells are defined by the argument \texttt{chisqbreaks}
or automatically defined from the data set and from the argument \texttt{meancount} (the approximate mean count per cell)
which is  fixed to $(4n)^{2/5}$ if omitted (with n the length of the data set).  
For more details, see the help of the function \texttt{fitdist}.
Four goodness of fit plots are also provided.

@@

Below is the result of another fit of the same distribution by matching moments.
<<>>=
f1gbis<-fitdist(x1,"gamma",method="mme")
summary(f1gbis)
@
